Adaption of the Chumbley Score to matching of bullet striation marks

### 2017-11-11 doc/paper.Rmd
couple of comments

@@

# Introduction

@@

## Existing solution for toolmarks: Chumbley Score

\hh{XXX anything to do with motivation has to come first - move this to the first paragraph of the intro XXX}
\hh{XXX data and results come after the intro to chumbley.}
\hh{XXX start with defining the data, i.e. we are working with random processes $x(t)$ and $y(t)$ ... you should also go into the coarseness parameter here - that is a pre-processing step before the optimization. }
\gk{done}

@@

## Chumbley Algorithm and Chumbley score

@@

## Potential limitations in the application to striation marks on bullet lands: smaller in width and curved - need to adjust parameter settings; something similar is done in \citet{afte-chumbley} for toolmark comparisons of slip-joint pliers.

@@

## Using cross-validation setup to identify appropriate parameter settings for (a) signatures and (b) profiles directly

Following on similar lines to the setup of toolamrks, the first step here is to first identify what difference does different window sizes of optimization and the validation step have, when adapting the toolmark method to bullets.

@@

>>>>

\tableofcontents

@@

# Introduction and Background

@@

## The Chumbley Score Test

\hh{You need to distinguish between $x(t)$ and $x(t_1)$ - $x(t)$ is a spatial process for some $t$. $x(t_1)$ is the realization of the process in $t_1$. - Alternatively you could also follow the notation in Hadler et al on 'digitized toolmarks at a pixel level' - where our 'pixel' is the resolution of the confocal light microscope, i.e. a pixel corresponds to 0.645 microns.}

@@

## Detailed algorithm

@@

## Potential limitations of the Chumbley Score

\hh{in the application to striation marks on bullet lands: smaller in width and curved - need to adjust parameter settings; something similar is done in \citet{afte-chumbley} for toolmark comparisons of slip-joint pliers. XXX work in }

@@

## Testing setup:
\hh{Using cross-validation setup to identify appropriate parameter settings for (a) signatures and (b) profiles directly}

Following on similar lines to the setup of toolmarks, the first step here is to first identify what difference does different window sizes of optimization and the validation step have, when adapting the toolmark method to bullets.

@@

## Discussion
